### 2013-09-23 clinical_significance.tex
fixed background reference

PCa screening has led to earlier diagnosis of smaller tumors and more localized
disease; however, it is well known that the sensitivity and specificity of PSA
and DRE are not optimal. In addition, DRE has a low predictive value at lower
PSA ranges, and PSA yields many false
positives.~\cite{Gosselaar2007,Gupta2013,Hricak2007} As such, a theoretical
risk of over-diagnosis and treatment of low-grade, and possibly clinically
insignificant, disease exists.  Moreover, due to the random nature of biopsies,
PCa located outside the routine sampling sites can be missed and the extent
of the cancer might be underestimated.~\cite{Gupta2013,Cornud1012} For example,
in a study by Mufarrij \etal, 45.9--47.2\% of patients who were candidates for
active surveillance, but underwent radical prostatectomy, had a higher Gleason
score on final histopathology than after TRUS biopsy.~\cite{Mufarrij2010} These
inaccuracies may lead to inappropriate diagnosis, imprecise risk assessment and
potentially avoidable morbidity.

>>>>

PCa screening has led to earlier diagnosis of smaller tumors and more localized
disease; however, it is well known that the sensitivity and specificity of PSA
and DRE are not optimal. In addition, DRE has a low predictive value at lower
PSA ranges, and PSA yields many false
positives.~\cite{Gosselaar2007,Gupta2013,Hricak2007} As such, a theoretical
risk of over-diagnosis and treatment of low-grade, and possibly clinically
insignificant, disease exists.  Moreover, due to the random nature of biopsies,
PCa located outside the routine sampling sites can be missed and the extent
of the cancer might be underestimated.~\cite{Gupta2013,Cornud2012} For example,
in a study by Mufarrij \etal, 45.9--47.2\% of patients who were candidates for
active surveillance, but underwent radical prostatectomy, had a higher Gleason
score on final histopathology than after TRUS biopsy.~\cite{Mufarrij2010} These
inaccuracies may lead to inappropriate diagnosis, imprecise risk assessment and
potentially avoidable morbidity.
